
% This LaTeX was auto-generated from MATLAB code.
% To make changes, update the MATLAB code and republish this document.

\documentclass{standalone}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage[framed, numbered]{matlab-prettifier}

\sloppy
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{0pt}

\begin{document}

    
    \begin{par}
Set of basic algebraic, analytic and trigonometric functions.
\end{par} \vspace{1em}


{\textbf{sinoids2angles}}

\begin{par}
Converts sinoids to angles.
\end{par} \vspace{1em}


{\textbf{angles2sinoids}}

\begin{par}
Converts angles to sinoids.
\end{par} \vspace{1em}


{\textbf{decomposeChol}}

\begin{par}
Performs a Cholesky Decomposition of a matrix to its lower triangle matrix. Returns logaritmic determinate of the matrix as side product.
\end{par} \vspace{1em}


{\textbf{frobeniusNorm}}

\begin{par}
Computes the Frobenius Norm of a matrix.
\end{par} \vspace{1em}


{\textbf{computeInverseMatrixProduct}}

\begin{par}
Computes the product of an inverted matrix A and a vector b or a matrix B by the represented lower triangle matrix L of Cholesky decomposed A.
\end{par} \vspace{1em}


{\textbf{computeTransposeInverseProduct}}

\begin{par}
Computes the both side porduct of an inverted matrix A with a vector b or matrix B (left product) and the transposed vector b or matrix B (right product).
\end{par} \vspace{1em}


{\textbf{addNoise2Covariance}}

\begin{par}
Additive noise for noisy GPR observations. Add noise along covariance matrix diagonal.
\end{par} \vspace{1em}


{\textbf{computeAlphaWeights}}

\begin{par}
Computes regression weights by residual of regression targets and regression mean values.
\end{par} \vspace{1em}


{\textbf{computeStdLogLoss}}

\begin{par}
Computes standardized logarithmic loss of test data and predicted data.
\end{par} \vspace{1em}


{\textbf{computeLogLikelihood}}

\begin{par}
Computes regression evidence as log marginal likelihood.
\end{par} \vspace{1em}


{\textbf{estimateBeta}}

\begin{par}
Compute polynom coefficients for mean approximation on training data.
\end{par} \vspace{1em}
\begin{par}
Created on February 14. 2021 by Tobias Wulf. Copyright Tobias Wulf 2021.
\end{par} \vspace{1em}
\begin{par}

\end{par} \vspace{1em}



\end{document}

