
% This LaTeX was auto-generated from MATLAB code.
% To make changes, update the MATLAB code and republish this document.

\documentclass{standalone}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage[framed, numbered]{matlab-prettifier}

\sloppy
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{0pt}

\begin{document}

    
    \begin{par}
Compute SLL loss between test targets and predictive mean dependend on predictive variance plus used variance for noisy covariance matrix as variance of normal distriubtion over predictive means s2 = fcov + s2n. The pred functions returns the standard deviation s so sqrt of the variance.
\end{par} \vspace{1em}

{\footnotesize\textbf{Contents}}

\begin{itemize}
\setlength{\itemsep}{-1ex}
   \item Syntax
   \item Description
   \item Input Argurments
   \item Output Argurments
   \item Requirements
   \item See Also
\end{itemize}


{\footnotesize\textbf{Syntax}}

\begin{lstlisting}[style=Matlab-editor, basicstyle=\ttfamily\scriptsize]
[SLL, SE, s2] = computeStdLogLoss(y, fmean, s)
\end{lstlisting}


{\footnotesize\textbf{Description}}

\begin{par}
\textbf{[SLL, SE, s2] = computeStdLogLoss(y, fmean, s)} compute standardized logaritmic loss by squared error of ideal test data predicted data and standard deviation of predicted data.
\end{par} \vspace{1em}


{\footnotesize\textbf{Input Argurments}}

\begin{par}
\textbf{y} column vector of ideal data to compare with.
\end{par} \vspace{1em}
\begin{par}
\textbf{fmean} column vector of predictive mean.
\end{par} \vspace{1em}
\begin{par}
\textbf{s} column vector of standard deviation related to predictive mean.
\end{par} \vspace{1em}


{\footnotesize\textbf{Output Argurments}}

\begin{par}
\textbf{SLL} column vector of standardized logarithmic loss.
\end{par} \vspace{1em}
\begin{par}
\textbf{SE} squared error between \textbf{y} and \textbf{fmean}.
\end{par} \vspace{1em}
\begin{par}
\textbf{s2} variance column vector.
\end{par} \vspace{1em}


{\footnotesize\textbf{Requirements}}

\begin{itemize}
\setlength{\itemsep}{-1ex}
   \item Other m-files required: None
   \item Subfunctions: log
   \item MAT-files required: None
\end{itemize}


{\footnotesize\textbf{See Also}}

\begin{itemize}
\setlength{\itemsep}{-1ex}
   \item \begin{verbatim}predFrame\end{verbatim}
   \item \begin{verbatim}predDS\end{verbatim}
   \item \begin{verbatim}lossDS\end{verbatim}
\end{itemize}
\begin{par}
Created on February 15. 2021 by Tobias Wulf. Copyright Tobias Wulf 2021.
\end{par} \vspace{1em}
\begin{par}

\end{par} \vspace{1em}
\begin{lstlisting}[style=Matlab-editor, basicstyle=\ttfamily\scriptsize]
function [SLL, SE, s2] = computeStdLogLoss(y, fmean, s)
    arguments
        % validate inputs as real column vectors of same length
        y (:,1) double {mustBeReal, mustBeVector}
        fmean (:,1) double {mustBeReal, mustBeVector, mustBeEqualSize(y, fmean)}
        s (:,1) double {mustBeReal, mustBeVector, mustBeEqualSize(y, s)}
    end
    % squared error
    SE = (y - fmean).^2;

    % s as standard deviation of nomal destributed fmean so square it for
    % variance.
    s2 = s.^2;

    % logaritmic error
    SLL = 0.5 * (log(2 * pi * s2) + SE ./ s2);
end

% Custom validation functions
function mustBeEqualSize(a, b)
    if ~isequal(length(a), length(b))
        eid = 'Size:notEqual';
        msg = 'Vectors must be the same length.';
        throwAsCaller(MException(eid,msg))
    end
end
\end{lstlisting}



\end{document}

