
% This LaTeX was auto-generated from MATLAB code.
% To make changes, update the MATLAB code and republish this document.

\documentclass{standalone}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage[framed, numbered]{matlab-prettifier}

\sloppy
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{0pt}

\begin{document}

    
    \begin{par}
That workflow describes a best practice way to simulate a sensor array with dipole (spherical magnet).
\end{par} \vspace{1em}
\begin{enumerate}
\setlength{\itemsep}{-1ex}
   \item Clean up old simuation datasets and plots of by executing   deleteSimulationDatasets and deleteSimulationPlots.
   \item Edit generateConfigMat to needed specifications for simulation and generate   or regenerate config.mat by executing the script.
   \item Execute generateSimulationDatasets to generate configure training and test   datasets.
   \item Execute the needed plots to describe the simulation as wished.
   \item Execute other parts of the software to work with current setup of simualtion   datasets.
   \item Rename plots or move them to a subfolder to save them.
   \item Move or rename Datasets if it is needed to keep them after done work.
   \item Restart workflow for a next configuration to investigate on.
\end{enumerate}

{\footnotesize\textbf{Contents}}

\begin{itemize}
\setlength{\itemsep}{-1ex}
   \item See Also
\end{itemize}


{\footnotesize\textbf{See Also}}

\begin{itemize}
\setlength{\itemsep}{-1ex}
   \item \begin{verbatim}generateConfigMat\end{verbatim}
   \item \begin{verbatim}deleteSimulationDatasets\end{verbatim}
   \item \begin{verbatim}generateSimulationDatasets\end{verbatim}
   \item \begin{verbatim}deleteSimulationPlots\end{verbatim}
\end{itemize}
\begin{par}
Created on December 03. 2020 by Tobias. Copyright Tobias 2020.
\end{par} \vspace{1em}
\begin{par}

\end{par} \vspace{1em}



\end{document}

